PineAPPL: combining EW and QCD corrections\\ for fast evaluation of LHC processes

### 2020-08-25 paper/paper.tex
Acknowledgements

\acknowledgments
We would like to thank Stefan Ditt\-mai\-er, Stefano Forte, Zahari Kassabov, and Juan Rojo for a critical reading of the manuscript, and we are grateful to Rikkert Frederix for discussions about \textsc{aMCfast}.
We acknowledge discussions with
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data.
S.C.\ and C.S.\ are supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
E.R.N.\ is supported by the European Commission through a Marie
Sk\l odowska-Curie Action (grant agreement no.\ 752748).
M.Z.\ thanks the Nikhef institute in Amsterdam,
where he was employed when this paper was started.

>>>>

\acknowledgments
We would like to thank Stefan Dittmaier, Stefano Forte, Zahari Kassabov, and Juan Rojo for a critical reading of the manuscript, and Rikkert Frederix for discussions about \textsc{aMCfast}.
We also acknowledge discussions with
Florencia Canelli, Stefano Camarda, Paolo Francavilla, Abideh Jafari, Andreas Jung, Elizaveta Shabalina, Wolfgang Wagner about the 
treatment of EW effects in experimental data.
S.C.\ and C.S.\ are supported by the European Research Council under the European Union's
Horizon 2020 research and innovation Programme (grant agreement no.\ 740006).
E.R.N.\ is supported by the European Commission through a Marie
Sk\l odowska-Curie Action (grant agreement no.\ 752748).
M.Z.\ thanks the Nikhef institute in Amsterdam,
where he was employed when this paper was started.
